Latin epigraphy for the visually impaired. New technologies to favour universal accessibility

### 2016-02-09 source/9/Latin epigraphy for the visually impaired.tex
added images for Licordari

@@

@@

@@

@@

@@

@@

@@

>>>>

\begin{figure}[!hbp]
\centering
 \includegraphics[width=\columnwidth]{1tactiletourVillaGiulia.JPG}
\caption{Sculptures are permitted to be touched in the National Etruscan Museum of Villa Giulia in Rome}
\label{fig:1}
\end{figure}

\begin{figure}[!hbp]
\centering
 \includegraphics[width=\columnwidth]{2resinreliefMonaLisa.JPG}
\caption{Resin relief of the Anteros Museum: Mona Lisa}
\label{fig:2}
\end{figure}

@@

\begin{figure}[!hbp]
\centering
 \includegraphics[width=\columnwidth]{3graphicprintBrailleMarcusUlpiusFructus.jpg}
\caption{The technical device of graphic Braille print for the panel of Marcus Ulpius Fructus}
\label{fig:3}
\end{figure}

@@

\begin{figure}[!hbp]
\centering
 \includegraphics[width=\columnwidth]{4thermoform.JPG}
\caption{The technique of the Thermoform with caption in Braille}
\label{fig:4}
\end{figure}

@@

\begin{figure}[!hbp]
\centering
 \includegraphics[width=\columnwidth]{5Minoltaheather.jpg}
\caption{Reproduction with printing granules (Minolta Heather) of the Cortona Triptych by Fra Angelico}
\label{fig:5}
\end{figure}

@@

\begin{figure}[!hbp]
\centering
 \includegraphics[width=\columnwidth]{6smallmodel3Dprinting.JPG}
\caption{Small model in 3D printing of the Sarcophagus of the Spouses}
\label{fig:6}
\end{figure}

\begin{figure}[!hbp]
\centering
 \includegraphics[width=\columnwidth]{7CloneSarcophagusoftheSpouses.jpg}
\caption{The clone of the Sarcophagus of the Spouses (scale 1:1) starting from the digital tridimensional scan of the
original Sarcophagus, Italdesign Giugiaro}
\label{fig:7}
\end{figure}

@@

\begin{figure}[!hbp]
\centering
 \includegraphics[width=\columnwidth]{8reproductionOstiaslighthouse.JPG}
\caption{The reproduction of the mosaic of Ostia’s lighthouse by the Federazione Nazionale delle Istituzioni Pro Ciechi NPO in the Square of the Corporations of Ostia Antica}
\label{fig:8}
\end{figure}

@@

\begin{figure}[!hbp]
\centering
 \includegraphics[width=\columnwidth]{9mosaicoftheLibyanboatmen.jpg}
\caption{The mosaic of the Libyan boatmen in Ostia Antica}
\label{fig:9}
\end{figure}

@@

\begin{figure}[!hbp]
\centering
 \includegraphics[width=\columnwidth]{10italicmirror.jpg}
\caption{A mirror from Praeneste  in the National Etruscan Museum of Villa Giulia in Rome}
\label{fig:10}
\end{figure}
